Inferring community characteristics in labelled networks

### 2021-05-19 nips/experiments.tex
Much work

We apply the developed methods to a variety of datasets, to show the power of the method across different scenarios. We choose a range of node counts $N$, edge counts $E$ and feature space dimension $D$.

@@

	\item \textbf{Facebook egonet} \cite{fb-snap} ($N=747, E=30025, D=480$) - an assortment of Facebook egonets. These are networks of a particular user's friends list and all the connections within that. Vertex features are extracted from each user's profile and is fully anonymized. We focus on the egonet with id 1912.

	\item \textbf{Maier Facebook Egonet} \cite{FB-Maier}  ($N=349, E=2336, D=32$) - egonet of the author's Facebook friends list. Each vertex has been manually labelled with a variety of features describing their relationship to the author. For our purposes we remove all nodes of degree 1 (those that are only connected to the egonode) as these cannot be said to be part of any community present in the graph.

	\item \textbf{Law firm} \cite{LawFirm} - a network of relationships between members of a law firm. Each relationship is categorised according to type: coworkers, friends or advice.

	\item \textbf{Twitch users} \cite{twitch} - a network of user-user friendships on the streaming service Twitch. Vertex labels are extracted according to video-games played, location and streaming habits. This dataset is also broken down into disjoint networks according to language. We only consider the English users with is a subnet with $N=7126$ vertices and $E=35324$ edges).

@@

We require metrics to assess the relative model evidence for the FFBM. . A table summarising the results is given in table \ref{tab:results}.

\begin{table}[!h]
	\centering
	\caption{FFBM fit for various datasets}
	\label{tab:results}
	\begin{tabular}{c|ccc|c|cc}
		Dataset & $N$ & $E$ & $D$ & $B$ & $\bar{S}_b /N$ & $\bar{U}_\theta /N$ \\ \hline
		Political books & 105  & 441 & 1 & 3 & 11.7 & 0.707 \\
		Primary school & 238 & 5539 & 13 &  18 & 43.0  & 2.75 \\
		Maier FB egonet &  &     &     &   &           &             \\

>>>>

We apply the developed methods to a variety of datasets, to show the power of the method across different scenarios. We choose datasets to span a range of node counts $N$, edge counts $E$ and feature space dimension $D$.

@@

	\item \textbf{Facebook egonet} \cite{fb-snap} ($N=747, E=30025, D=480$) - an assortment of Facebook egonets. These are networks of a particular user's friends list and all the connections within that. Vertex features are extracted from each user's profile and are fully anonymized. We focus on the egonet with id 1912.

%	\item \textbf{Maier Facebook Egonet} \cite{FB-Maier}  ($N=349, E=2336, D=32$) - egonet of the author's Facebook friends list. Each vertex has been manually labelled with a variety of features describing their relationship to the author. For our purposes we remove all nodes of degree 1 (those that are only connected to the egonode) as these cannot be said to be part of any community present in the graph.
%		
%	\item \textbf{Law firm} \cite{LawFirm} - a network of relationships between members of a law firm. Each relationship is categorised according to type: coworkers, friends or advice.
%	
%	\item \textbf{Twitch users} \cite{twitch} - a network of user-user friendships on the streaming service Twitch. Vertex labels are extracted according to video-games played, location and streaming habits. This dataset is also broken down into disjoint networks according to language. We only consider the English users with is a subnet with $N=7126$ vertices and $E=35324$ edges).

@@

We require metrics to assess the relative model evidence for the FFBM. This can be split into two separate components: the microcanonical SBM fit (concerned with the $b$-samples) and the fit of the feature-to-block generator (concerned with the $\theta$-samples). For each of these we can evaluate the mean of the unnormalised log-target of each Markov chain.
%
\begin{equation}
	\bar{S}_b \coloneqq \frac{1}{T_b} \sum_{t=1}^{T_b} S \left( b^{(t)} \right) \qquad \textrm{and} \qquad
	\bar{U}_\theta \coloneqq \frac{1}{T_\theta} \sum_{t=1}^{T_\theta} U \left( \theta^{(t)} \right)
\end{equation}
%
The lower these quantities, the better the fit of each stage of the model. To allow for rough comparison between datasets, we divide these quantities by the number of vertices in the graph $N$. Table \ref{tab:results} summarises the results for each experiment.

\begin{table}[!h]
	\centering
	\caption{FFBM fit for the datasets}
	\label{tab:results}
	\begin{tabular}{c|ccc|c|cc}
		Dataset & $N$ & $E$ & $D$ & $B$ & $\bar{S}_b /N$ & $\bar{U}_\theta /N$ \\ \hline
		Political books & 105  & 441 & 1 & 3 & 11.7 & 0.707 \\
		Primary school & 238 & 5539 & 13 &  18 & 43.0  & 2.75 \\
		FB egonet & 747 & 30025 & 480 & 10  &           &             \\

### 2021-05-19 nips/inference.tex
Much work

>>>>

\subsection{Dimensionality reduction}

Once we have the samples $\left\{ \theta^{(t)} \right\}_{t=1}^{T_\theta} \sim p(\theta | A, X)$, we can compute the empirical mean and standard deviation of each component of $\theta$. Switching back to matrix notation we define $\theta = W$, such that $W_{ij}$ is the weight component for block $i$ and feature $j$, we can define:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{T_\theta} \sum_{t=1}^{T_\theta} W_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma_{ij}} \coloneqq \frac{1}{T_\theta} \sum_{t=1}^{T_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2
\end{equation}
%
A simple heuristic to discard the least important features requires specifying a cutoff $c > 0$ and a multiplier $k > 0$. We then discard all features $j$ wuch that equation \ref{eqn:discard} is satisfied.
%
\begin{equation}
	(\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c) = \emptyset \quad \forall i \in \{1,2 \dots B\}
	\label{eqn:discard}
\end{equation}
%
Intuitively, this means discarding any feature for which $\hat{\mu}_{ij} \pm k\hat{\sigma_{ij}}$ lies within or spans the null region $(-c, c)$. If we were to use the Laplace approximation for the posterior $p(W_{ij} | A, X) \approx \Gaussian(W_{ij}; \mu_{ij}, \sigma_{ij})$, then this is effectively a hypothesis test on the value of $W_{ij}$.
%
\begin{equation}
	\begin{aligned}
		H_0&: |W_{ij}| \leq c \\
		H_1&: |W_{ij}| > c
	\end{aligned}
\end{equation}
%
With the multiplier $k$ specifying the degree of significance of the result (equivalent to the probability of a type-1 error). However, as the approximation is not exact we will only treat this dimensionality reduction method as a useful heuristic.
